---
title: "Ukrainian Martial Law Project Descriptive Statistics"
description: |
  This is the initial review of the basic statistical data from the martial law
  survey dataset.
author:
  - name: Kristina Becvar
    url: https://kristinabecvar.com
    affiliation: Human Security Lab
    affiliation_url: https://www.humansecuritylab.net/
date: 06-09-2022
output:
  distill::distill_article:
    self_contained: true
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(plyr); library(dplyr)
library(ggplot2)
library(cowplot)
library(broom)
library(scales)

```


# Variables

Variables for Ukraine Martial Law Demographic Data:

Region

Age

Age Group

Gender

Language

Education

Income Level

Response:

* *stay: “should be required to stay”*
* *flee: “should be permitted to flee”*
* *different: “my view different from either”*

# Data Analysis
```{r echo=FALSE}
#load the data
martial_data <- read_csv("martial-data.csv")
```

## General Observations

### Number of responses: "Flee", "Stay", or "Different"

```{r echo=FALSE}
table(martial_data$response)
```

### Respondent Mean Age

```{r echo=FALSE}
table(martial_data$age_group)
```

### Respondent Age Group Counts

```{r echo=FALSE}
table(martial_data$age_group)
```

### Respondent Gender Distribution

```{r echo=FALSE}
table(martial_data$gender)
```

### Respondent Language Distribution

```{r echo=FALSE}
table(martial_data$language)
```

### Respondent Education Distribution

```{r echo=FALSE}
table(martial_data$education)
```

### Respondent Income Level Distribution

```{r echo=FALSE}
table(martial_data$income)
```

## Summary Data

### Mean Age by Response

* Mean age for those choosing "Should have to stay" is 38.18
* Mean age for those choosing "Should be permitted to flee" is 35.78
* Mean age for those choosing a different response is 39.58

```{r echo=FALSE}
by(martial_data, martial_data$response, summary)
```

### Age Group by Response Type

```{r echo=FALSE}
table(martial_data$response, martial_data$age_group)
```

### Gender by Response Type

```{r echo=FALSE}
table(martial_data$response, martial_data$gender)
```

### Language by Response Type

```{r echo=FALSE}
table(martial_data$response, martial_data$language)
```

### Education by Response Type

```{r echo=FALSE}
table(martial_data$response, martial_data$education)
```

### Income Level by Response Type

```{r echo=FALSE}
table(martial_data$response, martial_data$income)
```

### Region by Response Type

```{r echo=FALSE}
table(martial_data$response, martial_data$region)
```



